The helicoverpa package

### 2021-08-19 notebook/helicoverpa_notes.Rmd
Fix typo in the notes

The helicoverpa package will be submitted to [CRAN](https://cran.r-project.org/) sometime before early August. What this will require is some appropriate testing functions and documentation, and maybe one or two vignettes that show how the package works. I'll also make a website similar to the [GMSE website](https://confoobio.github.io/gmse/). We will want to decide if the package name should actually be 'helicoverpa', or if we should switch to something else ([endorse](https://cran.r-project.org/package=endorse) is unfortunately taken; I'm not sure if 'ENDORSE' in all caps would work, but probably best to not try this and avoid confusion). I will update with more details about this later.

>>>>

The helicoverpa package will be submitted to [CRAN](https://cran.r-project.org/) sometime before early October What this will require is some appropriate testing functions and documentation, and maybe one or two vignettes that show how the package works. I'll also make a website similar to the [GMSE website](https://confoobio.github.io/gmse/). We will want to decide if the package name should actually be 'helicoverpa', or if we should switch to something else ([endorse](https://cran.r-project.org/package=endorse) is unfortunately taken; I'm not sure if 'ENDORSE' in all caps would work, but probably best to not try this and avoid confusion). I will update with more details about this later.
